### 2022-08-26 ersteops/templates/printpdf/paperless_template.tex
fix treatmen text

    %Impresion diagnostica
    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_diagnostic_impresion}}\end{tabular}}}}%
    %Tratamiento
    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_treatment}} \end{tabular}}}}%

>>>>

    %Impresion diagnostica
    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize {{content.fix_diagnostic_impresion}}\end{tabular}}}}%
    %Tratamiento
    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}{\fontfamily{lmss}\selectfont\scriptsize {{content.fix_treatment}} }\end{tabular}}}}%

### 2022-08-26 ersteops/templates/printpdf/rendered_template.tex
fix treatmen text

    %Impresion diagnostica
    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    %Tratamiento
    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA \end{tabular}}}}%

>>>>

    %Impresion diagnostica
    \put(0.51738337,0.45891074){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    %Tratamiento
    \put(0.75885924,0.45916877){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}{\fontfamily{lmss}\selectfont\scriptsize NA }\end{tabular}}}}%
